---
title: "EDA-Part 2"
output: html_document
---

For this exercise, I wanted to study the relationship between the fertility (children per woman) of a country and the expenditure on secondary eductaion

## Read and Tidy the secondary education expenditure data from xlsx file
```{r}

setwd('C:/Users/Sarah/Documents/R Files/EDA - Lesson 4/EDA Part 2 project files')
list.files()

library(rJava)
library(xlsxjars)
library(xlsx)
library(dplyr)
library(tidyr)
library(ggplot2)

se <- read.xlsx("expenditure secondary.xlsx", sheetIndex = 1, header= TRUE)
summary(se)
se <- gather(se, "year", "expenses", 2:length(colnames(se)))

names(se)[names(se) == "Expenditure.per.student..secondary....of.GDP.per.capita."] <- "country"
se$year <- gsub("X", "", se$year)


cpw <- read.xlsx("indicator undata total_fertility.xlsx", sheetName = "Data", header = TRUE)  
cpw <- gather(cpw, "year", "fertilityRate", 2:length(colnames(cpw)))

names(cpw)[names(cpw) == "Total.fertility.rate"] <- "country"
cpw$year <- gsub("X", "", cpw$year)
View(cpw)
View(se)


totalData <- inner_join(se, cpw, by = c('country','year'))
totalData <- totalData[complete.cases(totalData),]

?complete.cases
View(totalData)
rm(se, cpw)

ggplot(data = totalData, aes(x = fertilityRate, y = expenses)) +
  geom_point()

ggplot(data = totalData, aes(x = fertilityRate, y = expenses)) +
  geom_point(alpha = 1/4) +
  xlab("Number of childern per woman") +
  ylab("Secondary Education expenditure as % of GDP") +
  ylim(0,100) +
  ggtitle("Secondary Education expenditure Vs. Fertility Rate")

cor.test(totalData$expenses, totalData$fertilityRate)

ggplot(aes(x=fertilityRate, y = expenses), data = totalData) +
  xlab("Number of childern per woman") +
  ylab("Secondary Education expenditure as % of GDP") +
  ylim(0,100) +
  geom_line(aes(color = country), show.legend = FALSE)
  
```

The relationship between fertility rate and secondary Education expenditure as % of GDP is different for different countries. Let us examine it more closely for a few countries


```{r, echo=FALSE}
sampleCountries <- totalData[ which(totalData$country %in% c("India", "Brazil", "United States", "Denmark", "Japan")),]

ggplot(aes(x=fertilityRate, y = expenses), data = sampleCountries) +
  geom_line(aes(group = country)) +
  facet_wrap(~country, scales = "free_y") 




```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
